ITHIM

### 2022-01-19 latex/output-md.Rmd
Update text

The relationships comes out of our work @Leandro2018, where we look at the association of `physical activity` with various diseases.

@@

We resample the adjusted probability parameters of Table [6](#calculations){reference-type="ref" reference="calculations"}. We describe each parameter with a Beta distribution as follows: $$\begin{aligned}
\label{pitilde}
\tilde{B}_{a,g,m} & \sim \text{Beta}(\alpha_{a,g,m},\beta_{a,g,m}); \\
\alpha_{a,g,m}+\beta_{a,g,m} & = 200; \\
\hat{B}_{a,g,m} & = \frac{1}{1+\frac{\beta_{a,g,m}}{\alpha_{a,g,m}}}.\end{aligned}$$ Here, $\tilde{B}_{a,g,m}$ is the new, variable parameter that we resample for each simulation. We sample via a quantile, $\nu_m\sim\mathcal{U}(0,1)$, which we use to calculate $\tilde{B}_{a,g,m}$. We set $\alpha_{a,g,m}$ and $\beta_{a,g,m}$ to sum to 200, making the distributions concentrated, and we constrain their relative values to enforce the distribution's mean to equal $\hat{B}_{a,g,m}$ (the right-most column in Table [6](#calculations){reference-type="ref" reference="calculations"}).

>>>>

The relationships comes out of our work on meta-analyses \@Leandro2018, where we look at the association of `physical activity` with various diseases.

@@

We resample the adjusted probability parameters of Table [6](#calculations){reference-type="ref" reference="calculations"}. We describe each parameter with a Beta distribution as follows:

\$$\hat{B}_{g,m} \tilda L_m{B}_{a,g,m}.$$

Ba,g,m∼Beta(αa,g,m,βa,g,m);

\label{pitilde}

\$$\hat{B}_{a,g,m} & \sim \text{Beta}(\alpha_{a,g,m},\beta_{a,g,m}); \\$$

${\hat{B}}_{a,g,m} \sim Beta({\alpha}_{a,g,m}, {\beta}_{a,g,m})$
${\alpha}_{a,g,m} + {\beta}_{a,g,m} = 200$
$\hat{B}_{a,g,m} & = \frac{1}{1+\frac{\beta_{a,g,m}}{\alpha_{a,g,m}}}$

\alpha_{a,g,m}+\beta_{a,g,m} & = 200; \\
\hat{B}_{a,g,m} & = \frac{1}{1+\frac{\beta_{a,g,m}}{\alpha_{a,g,m}}}.\end{aligned}$$ Here, $\tilde{B}_{a,g,m}$ is the new, variable parameter that we resample for each simulation. We sample via a quantile, $\nu_m\sim\mathcal{U}(0,1)$, which we use to calculate $\tilde{B}_{a,g,m}$. We set $\alpha_{a,g,m}$ and $\beta_{a,g,m}$ to sum to 200, making the distributions concentrated, and we constrain their relative values to enforce the distribution's mean to equal $\hat{B}_{a,g,m}$ (the right-most column in Table [6](#calculations){reference-type="ref" reference="calculations"}).
